---
title: "study 4 data analysis"
output:
  rmdformats::material:
    code_folding: hide
    css: "style.css"

---
# Tidy data

## Set-up
```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(kableExtra)
library(knitr)
library(plotly)
library(broom)
library(wesanderson)
library(robust)
library(ggparl)

```
## Read data
```{r read_data}
# reads excel data sheet

data <- read.csv("../data/study4.csv") # reads data
data_sat <- read.csv("../data/raw/stage3_satisfaction.csv") # reads in satisfaction data



# summary(data) # explore the data types, missing data and typos

data <- data %>%
  mutate(gender = ifelse(gender == "m", "m", "f")) # corrects an issuewith extra space in "f "

data$gender <- as.factor(data$gender)
data$pp_number <- as.factor(data$pp_number)
data$condition <-as.factor(data$condition)


# mood data
mood1 <- read.csv("../data/raw/stage1_mood.csv") %>%
  select(subject, stimulusitem2, response)%>%
  rename(response1=response, feeling = stimulusitem2)%>%
  mutate(stage = 1)

mood2 <- read.csv("../data/raw/stage2_mood.csv") %>%
  select(subject, stimulusitem2,  response)%>%
  rename(response2=response,  feeling = stimulusitem2)%>%
  mutate(stage = 2)

mood3 <- read.csv("../data/raw/stage3_mood.csv") %>%
  select(subject, stimulusitem2, response) %>%
  rename(response3=response,  feeling = stimulusitem2)%>%
  mutate(stage = 3)


# qualtrics data 
      #mainly info about drinking

data_q <- read.csv("../data/other/study_4Q.csv")%>%
  select(Q21, gender, age, Q15, Q16)%>%
  rename(subject = Q21, 
         units = Q15, 
         units_beer = Q16)%>%
  mutate(subject = as.numeric(subject),
         condition = subject %/% 1000)%>%
  filter(!is.na(subject))%>%
  mutate(subject = as.factor(subject), 
         gender=as.factor(gender), 
         age = as.numeric(age), 
         units = as.numeric(units), 
         units_beer = as.numeric(units_beer))%>%
  filter( subject != "6666")




```
## Data joins
```{r joining data}

DA <- data %>%
  select(pp_number, BMI)%>%
  rename(subject = pp_number)

DB <- data_sat %>%
  select(subject, response, trialcode ) %>%
  mutate(row = row_number(), subject = as.factor(subject)) %>%
  pivot_wider(names_from = trialcode, values_from = response) %>%
  rename( wtp = VAS_wtp)%>%
  select(- row)


D1 <- inner_join( DA,DB,
                  by = "subject",
                  keep = FALSE
                ) %>%
    pivot_longer(cols =c(VAS, wtp) , 
                 names_to = "measure", 
                 values_to = "rating") %>%
    inner_join(., data_q,
             by = "subject", 
             keep = FALSE)%>%
  filter(!is.na(rating))
                                            # long dataset incl,. info about satisfaction and willingness to pay by condition, and alcohol/ non-alcohol
# need to add focus condition


#Joining mood data

D2 <- inner_join(mood1, mood2, 
                 by = c("subject", "feeling"),
                 keep = FALSE) %>%
  inner_join(., mood3,
             by = c("subject","feeling"),
             keep = FALSE)%>%
            select(- starts_with("stage")) %>%
  mutate(condition = subject  %/% 1000) %>%
  pivot_longer(cols = starts_with("response"),
   names_to = "stage",
   names_prefix = "response",
   values_to = "rating")
  
                 

```


# Descriptive analyses

## Differences between conditions

```{r pp descriptives}

# gender
total_n <- nrow(data)
males <- data_q%>%filter(gender == "male") %>% nrow()
females <- data_q%>%filter(gender == "female") %>% nrow()
nonbinary <- data_q %>% filter(gender== "non-binary" )%>% nrow()



# by condition
gender_tib <- D1 %>% 
  filter(measure == "wtp") %>% # avoids duplicating data
  group_by( condition) %>%
  summarise(n=n(),
            BMI = mean(BMI, na.rm = TRUE), 
            age = mean(age, na.rm = TRUE)) %>% 
  kable()


```

### Gender

```{r gender_conditions}
xtabs(~ gender + condition , data = data_q,drop.unused.levels = TRUE)%>%
  kable(digits = 2, caption = "A contingency table with observed gender values/counts across conditions") %>%
  kable_styling(full_width = TRUE, 
                position = "left")

chi_test <- chisq.test(data_q$gender, data_q$condition, simulate.p.value = TRUE)

chi_test$expected %>%
  kable(digits = 1, caption = "A contingency table of expected gender values/counts across conditions")%>%
  kable_styling(full_width = TRUE,
                position = "left")
  

#  χ2 test requires all expected frequencies to be greater than five --> simulate.p.value avoids the problem

```

Altogether `r total_n` participants took part in the study, as is common for psychology studies, most of these were women (`r females` self-identified as female, `r males` as male and `r nonbinary` as non-binary). The gender split across the conditions was not problematic $\chi^2$ = `r round(chi_test$statistic,2)`, *p* = `r round(chi_test$p.value,3)` (simulated *p* values based on 2000 replicates, as expected values << 5).


```{r gender_conditions_plot, fig.cap= "Number of participants in each conditions"}
# plot
## bar plot is best here
gender_pal <- c("#d62828", "#003049", "#9d69a3")
gender_cond_plot <-
  ggplot(data = data_q)+
  geom_bar(aes(x= condition, fill = gender))+
  scale_fill_manual(values = gender_pal) +
  scale_y_continuous(name="", limits=c(0, 40), breaks = seq(0,40, 5)) +
  scale_x_discrete(name = "conditions", breaks = seq(1,6,1), limits = c("1", "2", "3", "4", "5", "6"))+
  theme(panel.grid = element_blank())+
  theme_minimal()

 ggplotly(gender_cond_plot)  

```

### Age
```{r age_conditions}
data_desc <- D1 %>%
  filter(measure == "wtp")

age_lm <- lm(age ~ condition, data=data_desc)

age_sum <- broom::tidy(age_lm)
age_glance <- broom::glance(age_lm)
```

Participants' age ranged between `r min(data_desc$age, na.rm = TRUE)` and `r max(data_desc$age, na.rm = TRUE)`. Most participants were very young and the mean age of participants was `r round(mean(data_desc$age, na.rm = TRUE),1)` (*sd* = `r round(sd(data_desc$age, na.rm = TRUE),1)`). The age did not significantly differ across the six conditions F(`r age_glance$df.residual`, `r age_glance$df`) = `r round(age_glance$statistic,2)`, *p* = `r round(age_glance$p.value,3)`.

```{r age, fig.cap= "Participants' age by condition and gender. Note range of the y-axis "}


age_plot <- ggplot(data= data_desc, aes(x=condition, y = age, group = condition) )+
  geom_boxplot(fill= "#6c757d", alpha = 0.5, outlier.shape = NA) +
  geom_jitter(shape=16, position=position_jitter(0.2), aes(color = gender))+
  scale_y_continuous(name="age", limits=c(18, 60), breaks = seq(0,60, 10)) +
  scale_x_discrete(name = "conditions", limits = c("1", "2", "3", "4", "5", "6"))+
  scale_color_manual(values = gender_pal) +
  theme_minimal()

age_plot2 <- ggplot(data= data_desc, aes(x=condition, y = age, group = condition) )+
  geom_boxplot(fill= "#6c757d", alpha = 0.5, outlier.shape = NA) +
  geom_jitter(shape=16, position=position_jitter(0.2), aes(color = gender))+
  scale_y_continuous(name="age", limits=c(15, 30), breaks = seq(15,30,5)) +
  scale_x_discrete(name = "conditions", limits = c("1", "2", "3", "4", "5", "6"))+
  scale_color_manual(values = gender_pal) +
  theme_minimal()

ggplotly(age_plot)
ggplotly(age_plot2)
```


### BMI
```{r BMI_conditions}

bmi_lm <- lm(BMI ~ condition, data=data_desc)

bmi_glance <- broom::glance(bmi_lm)

```

The participants' BMI ranged between `r round(min(data_desc$BMI, na.rm = TRUE),1)` - `r round(max(data_desc$BMI, na.rm = TRUE),1)`. The average BMI was `r round(mean(data_desc$BMI),1)` (*sd* =`r round(sd(data_desc$BMI),1)`) and again, this did not differ across conditions F(`r bmi_glance$df.residual`, `r bmi_glance$df`) = `r round(bmi_glance$statistic,2)`, *p* = `r round(bmi_glance$p.value, 3)`.

```{r BMI, fig.cap=" Participants' BMI by condition and gender"}
BMI_plot <- ggplot(aes(x=condition, y = BMI), data= data_desc)+
  geom_boxplot(fill= "#6c757d", alpha = 0.5) +
  geom_jitter(shape=16, position=position_jitter(0.2), aes(color = gender))+
  scale_y_continuous(name="BMI", limits=c(18, 35), breaks = seq(0,35, 10)) +
  scale_x_discrete(name = "conditions", limits = c("1", "2", "3", "4", "5", "6"))+
  scale_color_manual(values = gender_pal) +
  theme_minimal()

ggplotly(BMI_plot)

```



### Baseline mood

Visual inspection of participants' baseline mood does not give raise to any concerns. *Do I need to run 16 anovas? Does not seem necessary...)*
```{r mood_conditions_plot, fig.cap= "Participants' baseline mood ratings"}
mood_base <- D2 %>%
  filter(stage == 1)

palette <- c("#033f63","#28666e","#7c9885","#b5b682","#fedc97","#e5e1ee","#c17767","#210203","#eb9486","#82204a", "#0a2342","#2ca58d","#84bc9c","#fffdf7","#f46197","#fec601")

ggplot(data = mood_base, aes(x=condition, y = rating, group = condition, fill = feeling))+
  geom_boxplot()+
  facet_wrap("feeling")+
  scale_fill_manual(values = palette) +
  scale_y_continuous(name="", limits=c(0, 100), breaks = seq(0,100, 20)) +
  theme(panel.grid = element_blank())+
  theme_minimal()
  

```


### Drinking

#### alcohol consumption

```{r alcohol_consumption, include = FALSE}
pp_over14units <-data_q%>%filter(units>14)%>%nrow() # no. of pp consuming more than 14 units of alcohol a week

# statistical analysis

al_cons_lm <- lmRob(units ~ condition, data= data_q)
al_model<-summary(al_cons_lm)
al_a<-anova(al_cons_lm)

beer_cons_lm <-lmRob(units_beer ~ condition, data = data_q)
beer_model<-summary(beer_cons_lm)
beer_a<-anova(beer_cons_lm)
```
While the average alcohol consumption was realtively low `r round(mean(data_q$units),1)` (*sd* = `r round(sd(data_q$units),1)`), there was a considerable differences among participants. The lowest alcohol consumption was only `r min(data_q$units)`, equivalent to a half a pint of light beer (3.5%) once a week, the highest alcohol consumption was `r max(data_q$units)` units of alcohol a week, which is equivalent to over 20 pints of strong (~5% abv) beer every week. Interestingly, `r pp_over14units ` (`r round((pp_over14units/total_n)*100,1)`%) participants consumed more than the recommended 14 units a week. We also asked participants to estimate how many units of beer they consumed. This was on average `r round(mean(data_q$units_beer),1)` (*sd* = `r round(sd(data_q$units_beer),1)`), this  however varied between `r min(data_q$units_beer)` and  `r max(data_q$units_beer)`. Thefigures below show participants' weekly alcohol consumption, weekly beer consumption and the proportion of units of alcohol that came from beer. Neither the overall alcohol consumption nor beer consumption differed significantly across the conditions, F(`r al_model$df[1] `, `r al_model$df[2] `) = `r round(al_a$RobustF[2],2)`, *p* = `r round(al_a$"Pr(F)"[2],3)` and F(`r beer_model$df[1] `, `r beer_model$df[2] `) = `r round(beer_a$RobustF[2],2)`, *p* = `r round(beer_a$"Pr(F)"[2],3)`, respectively. 

```{r alcohol_plot, fig.cap="participants' alcohol consumption by condition"}

# plot units alcohol consumption by condition

units_plot<-ggplot(aes(x=condition, 
           y = units, 
           group = condition), 
           data= data_q)+
  geom_hline(aes(yintercept = 14, linetype = "14 units/week"),
             color = "red")+
  scale_linetype_manual(name = "max. recommended\nalcohol consumption", values = c(2, 2),
                      guide = guide_legend(override.aes = list(color = c("red")), title.theme = element_text(size = 8, face = "bold" ) ))+
  geom_boxplot(fill= "#6c757d", 
               alpha = 0.5, 
               outlier.shape = NA) +
  geom_jitter(shape=16, 
              position=position_jitter(0.2), 
              aes(color = gender))+
  scale_y_continuous(name="alcohol consumption\n(units)", 
                     limits=c(0, 75), 
                     breaks =   seq(0,75, 5)) +
  scale_x_discrete(name = "conditions", 
                   limits = c("1", "2", "3", "4", "5", "6"))+
  scale_color_manual(values = gender_pal) +
  theme_minimal()

ggplotly(units_plot)

```

```{r beer_plot, fig.cap="participants' beer consumption by condition"}
# plot units beer consumption by condition

beer_plot<-ggplot(aes(x=condition, 
           y = units_beer, 
           group = condition), 
           data= data_q)+
  geom_boxplot(fill= "#6c757d", 
               alpha = 0.5, 
               outlier.shape = NA) +
  geom_jitter(shape=16, 
              position=position_jitter(0.2), 
              aes(color = gender))+
  scale_y_continuous(name="beer consumption\n(units)", 
                     limits=c(0, 35), 
                     breaks =   seq(0,35, 5)) +
  scale_x_discrete(name = "conditions", 
                   limits = c("1", "2", "3", "4", "5", "6"))+
  scale_color_manual(values = gender_pal) +
  theme_minimal()

ggplotly(beer_plot)

```

```{r beer_prop_plot, fig.cap="% of alcohol consumption that is beer by condition"}

summary_beer <- data_q %>%
   pivot_longer(cols = starts_with("units"),  names_to = "al_id", values_to = "units") %>%
   mutate(al_id = ifelse(al_id =="units", "all", "beer"))%>%
   group_by(condition, al_id)%>%
   summarize(units = mean(units))%>%
  pivot_wider(names_from = al_id, values_from = units)%>%
  mutate(perc= (beer/all)*100)%>%
  pivot_longer(cols = c(all, beer), names_to = "alcohol", values_to = "units")

al_pal <- c( "#1d3557","#f4a261")
  
beer_prop <- ggplot(data=summary_beer, 
       aes(x=condition,
           y=units, 
           fill = alcohol)) +
  geom_bar(stat="identity", 
           position=position_dodge())+
  geom_text(aes(label =paste0(round(perc,1),"%") ), 
             data = summary_beer %>%filter(alcohol == "beer"), 
             show.legend = FALSE,
             size = 2, 
             nudge_x = 0.3, 
             nudge_y = 1,
             color = "#1d3557" )+
  scale_fill_manual(values = al_pal)+
  scale_y_continuous(name="alcohol consumption\n(units)", 
                     limits=c(0, 15), 
                     breaks =   seq(0,15, 5)) +
  scale_x_discrete(name = "conditions", 
                   limits = c("1", "2", "3", "4", "5", "6"))+
  labs( fill = "alcohol")+
  theme_minimal()

ggplotly(beer_prop)
```

# Expectations & Gustatory Perception

## Bitterness

## Refreshment

## Liking

## Body
